\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-28 papers/jfp/5-rebuilders.tex
Describe how to build a dirty bit builder

\q{Andrey}{Can we say something like: ``The authors are not aware of a build
system that uses a dirty bit rebuilder, is minimal, and supports the early
cutoff optimisaion''? Perhaps, we can even make a claim, that such a build
system is impossible with a believable argument/proof sketch?}

>>>>

It is possible to write a dirty-bit builder which is minimal and supports early
cutoff. To do so, you need to start with all inputs that have changed marked dirty,
then a node must be rebuilt if any children are dirty, and must set that node to dirty
only if the result changes. At the end of the build all dirty bits
must be reset to not-dirty. This approach only works if all targets are rebuilt each time,
since clearing dirty bits of children who aren't targets will cause them to incorrectly
not rebuild subsequently. To avoid resetting the dirty bit,
it is possible to use successive execution numbers, which ultimately leads to an approach
we call verifying step traces in \S\ref{sec-step-traces}.
